---
title: "Using simulate CC"
author: "LAURA PAABY and DANIEL BLUMENKRANZ"
date: "2023-12-04"
output: html_document
---

### Simulating data using the function in Simulate_Func.R

```{r}
getwd()
```


```{r}
source("Simulate_FUNC.R")
```


# Setting the parameters space from which we will simulate:
```{r} 
ntrials <- 1000
```

### Alpha 
$\alpha$ = Initial belief about others’ contribution
- based on this I suggest lambda = 5
```{r}
alpha <- c(1:10) # dictates the initial contribution of others (should be 0,3,6,9) => can either be manipulated somehow ?? or 0,1,2,3 and the rescaled. 

desired_values <- c(0, 3, 6, 9) # trying for the dist to only holds these
```


```{r}
for (i in alpha){
  dist <- rpois(ntrials, lambda=i) 
  filtered_values <- dist[dist %in% desired_values] # this is a very un-elegant way - cause samples for all but we pick the once we want 
  hist(filtered_values, main = (sprintf("lambda = %s",i)))
}

```



### Rho 
$\rho$ = Conditional preferences or readiness to cooperate
Is between 0 and 1.

```{r}
shape1 = c(1:5)
shape2 = c(1:5)
  

for (i in shape1){
  for (t in shape2){
    rho_samples <- rbeta(n = ntrials, shape1 = i, shape2 = t) # this isn't plotted but it gives the values 
    curve(dbeta(x, shape1 = i, shape2 = t), from = 0, to = 1, 
    xlab = "x", ylab = "Density", main = (sprintf("shape1 = %s, shape2 = %s",i,t)))
  }
}

?dbeta
```

```{r}
#print(rho_samples)
##### this is not so good - we need them to be stored in another way - they are just added one top of each other in the loop, but we need to do it in a way in which we can identify their shape parameters 
```

### Omega
$\omega$ = Sensitivity or attentiveness to others’ contributions


```{r}
shape1 = c(3:8)
shape2 = c(1:5)

for (i in shape1){
  for (t in shape2){
    omega_samples <- rbeta(n = ntrials, shape1 = i, shape2 = t) # this isn't plotted but it gives the values 
    curve(dbeta(x, shape1 = i, shape2 = t), from = 0, to = 1, 
    xlab = "x", ylab = "Density", main = (sprintf("shape1 = %s, shape2 = %s",i,t)))
  }
}

?dbeta
```


#### thought 
- we need to figure out if there is anything that should determine these shapes? Josh uses nations, maybe maltreaded vs. treated can be used?