---
title: "Using simulate CC"
author: "LAURA PAABY and DANIEL BLUMENKRANZ"
date: "2023-12-04"
output: html_document
---

### Simulating data using the function in Simulate_Func.R

```{r}
getwd()
```


```{r}
pacman::p_load(extraDistr, tidyverse, truncnorm, cascsim)
```


```{r}
source("Simulate_FUNC.R")
```


# Setting the parameters space from which we will simulate:
```{r} 
ntrials <- 1000
```

### Alpha 
$\alpha$ = Initial belief about others’ contribution
- based on this I suggest lambda = 5


```{r}
alpha<- c(0.6, 1.5, 3, 5) # dictates the initial contribution of others (should be 0,3,6,9) => can either be manipulated somehow ?? or 0,1,2,3 and the rescaled.
```


```{r}
#### inspecting the poisson probability distribution by calculating the probability at each point using dtpois

range = 0:3
par(mfrow=c(1,4))
for (i in alpha){
  p <- extraDistr::dtpois(range, lambda=i, a = -1, b = 3)
  #plot(range, p, main = paste("alpha =", i), type = 'h', lwd = 5)
  barplot(p, main = paste("alpha =", i), names.arg = c(0,1,2,3))
}

```

Play around with regular poisson.
```{r}
alpha<- c(0.6, 1.5, 3, 5)

# plot the regular poisson distribution for each lambda
range = 0:10
par(mfrow=c(1,4))
for (i in alpha){
  p <- dpois(range, lambda=i)
  barplot(p, main = paste("alpha =", i), names.arg = range)
}


```

Find a reasonable gamma distribution for mid_alpha
```{r}
# plot PDF of gamma distribution
x <- seq(0, 10, length.out = 1000)
y <- dgamma(x, shape = 2, rate = 1)
y1 <- dgamma(x, shape = 4, rate = 2)
y2 <- dgamma(x, shape = 6, rate = 3)
plot(x, y, type = "l", lwd = 2, col = "blue", xlab = "x", ylab = "PDF", ylim=c(0,0.7))
lines(x, y1, lwd = 2, col = "red")
lines(x, y2, lwd = 2, col = "green")
```
Find a reasonable normal distribution for diff_alpha
```{r}
# plot PDF of normal distribution
x <- seq(-2, 2, length.out = 1000)
y <- dnorm(x, mean = 0, sd = .1)
y1 <- dnorm(x, mean = 0, sd = .15)
y2 <- dnorm(x, mean = 0, sd = .2)
plot(x, y, type = "l", lwd = 2, col = "blue", xlab = "x", ylab = "PDF", ylim=c(0,0.7))
lines(x, y1, lwd = 2, col = "green")
lines(x, y2, lwd = 2, col = "red")
```
```{r}
samples <- truncnorm::rtruncnorm(1000, a=1, b=4, mean=2.5, sd=0.5)
hist(samples, breaks = 20)
```




```{r}
x <- seq(0, 100, length.out = 1000)
y <- dgamma(x, shape = 1, rate = 0.01)
y1 <- sqrt(1/y)
#par(mfrow=c(2,1))
plot(x, y, type = "l", lwd = 2, col = "blue", xlab = "x", ylab = "PDF")
#plot(y, y1, type = "l", lwd = 2, col = "red", xlab = "x", ylab = "PDF", ylim = c(0,10))
```





### Rho 
$\rho$ = Conditional preferences or readiness to cooperate
Is between 0 and 1.

```{r}
rho <- seq(from = 0.1, to = .90, by =.1)
rho

```

```{r}
x <- seq(0.001, 0.999, length.out = 1000)
y <- dbeta(x,shape1 = 1, shape2 = 1)
plot(x, y, type = "l", lwd = 2, col = "blue", xlab = "x", ylab = "PDF")
```


### Omega
$\omega$ = Sensitivity or attentiveness to others’ contributions
```{r}
omega <- seq(from = 0.1, to = .90, by =.1)
omega
```


# LOOPING OVER THE PARAMETERS TO SIMULATE:
```{r}
source("Simulate_FUNC.R")


empty_frame <- data.frame()

for (a in alpha){
  for (r in rho){
    for (o in omega){
      
    contri <- hier_cc_sim(a,r,o)  
  
    new_row <- c(a, r, o, contri)
    empty_frame <- rbind(empty_frame, new_row) 
    }
  }
}
```



#### subset for plotting:
```{r}
plot_dat <- empty_frame %>% 
  select(-c("X0", "X1", "X0.1"))

plot_wide <- t(plot_dat) 

col <- data.frame(1:12)

dat <- cbind(plot_wide, col) %>% 
  rename(trial = "X1.12")
```


```{r}

plot(x = dat$trial, y = dat$`1`, type = "l", ylim = c(0,5))

for (s in seq(2:1331)){
  lines(x = dat$trial, y= dat$`s`)
}
```



```{r}
dat_col <- colnames(dat)

dat %>% 
  ggplot(aes(x = trial, y = dat_col[0:10])) +
  geom_line()


dat %>%
  gather(key = "variable", value = "value", 1:100) %>%
  ggplot(aes(x = trial, y = value, color = variable)) +
  geom_line()
```



# Group simulations by HIER func:
making the population mean - this is done by taking the median of the possible values each of the parameters can hold 
(this solely our decision - no theory sorry)
```{r}
#### find the true pop mean 
pop_alpha <- 3 # this is the mean between 1-5
pop_rho <- .5
pop_omega <- .5 

#### lets now define the difference that might be between the group parameters:
dif_alpha <- seq(0,2,.20)
dif_rho <- seq(0,.75,.10)
dif_omega <- seq(0,.75,.10)

#### number of simulations
nsims <- 100

#### sigma 
sigma_alpha <- 1.25
sigma_omega <- .25
sigma_rho <- .25

```


# Run the simulation:

```{r}
source("HIER_simulation_FUNC.R")
```

```{r}
compute_mean <- function(pop_mean, dif, mt=FALSE){
  if (mt){  mean = pop_mean - (dif/2) }
  else { mean = pop_mean + (dif/2) }
  
  return(mean)
}
```


#### MT_


```{r}
nmt_dat <- list()
mt_dat <- list()

for (i in 1:nsims){
  
  # sample group difference for all params
  dif_alpha <- runif(1,0,2)
  dif_rho <- runif(1, 0, .75)
  dif_omega <- runif(1, 0, .75)
  
  # calculate group means
  nmt_mu_alpha <- compute_mean(pop_alpha, dif_alpha)
  mt_mu_alpha <- compute_mean(pop_alpha, dif_alpha, mt=T)
  
  nmt_mu_rho <- compute_mean(pop_rho, dif_rho)
  mt_mu_rho <- compute_mean(pop_rho, dif_rho, mt=T)
  
  nmt_mu_omega <- compute_mean(pop_omega, dif_omega)
  mt_mu_omega <- compute_mean(pop_omega, dif_omega, mt=T)
  
  ##### ---------- RUNNING THE FUNCTION  ------------ ##### 
  nmt_contris <- hier_cc_sim(150, nmt_mu_alpha, nmt_mu_rho, nmt_mu_omega, sigma_alpha, sigma_rho, sigma_omega)
  
  nmt_dat[[i]] <- nmt_contris
  
  mt_contris <- hier_cc_sim(150, mt_mu_alpha, mt_mu_rho, mt_mu_omega, sigma_alpha, sigma_rho, sigma_omega)
  
  mt_dat[[i]] <- mt_contris
  
}

```


##### plotting:
```{r}

```











